Forecasting the 2024 U.S. Presidential Election: A Poll-of-Polls Approach for Predicting the Outcome

### 2024-11-04 paper/paper.qmd
Appendix and referencebib update

# Load required libraries
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
library(arrow)  # Ensure arrow is loaded to use read_parquet()

@@

#result

@@

```
The national average support percentages, along with other summary statistics for Donald Trump and Kamala Harris, are summarized in @tbl-1. This table presents average support, standard deviation, and the range of polling support values for each candidate, providing insights into the predicted national favorability for both candidates.

@@

# Plot the map showing support difference
ggplot(map_data, aes(long, lat, group = group, fill = support_diff)) +
  geom_polygon(color = "white") +
  scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0, 
                       name = "Support Difference\n(Harris - Trump)") +
  theme_minimal() +
  theme(legend.position = "right")
```
@fig-figure1 visualizes the difference in average polling support between Kamala Harris and Donald Trump across U.S. states. The map uses a color gradient to convey where each candidate has more support, with shades of blue indicating higher support for Harris, red indicating higher support for Trump, and white representing near-equal support levels. This visual provides a geographic perspective on the polling landscape, highlighting regional strongholds, competitive states, and areas of significant support advantage for each candidate.

@@

```
@fig-figure2 visualizes the polling margins between the top two candidates in various states. Each bar represents a state, with the length of the bar corresponding to the polling margin—the difference in polling percentage between the leading candidate and the runner-up. States are ordered by margin, from the narrowest at the bottom (indicating the closest contest) to the widest margin at the top. For instance, states like Arizona, Minnesota, and Michigan show extremely close polling margins, meaning that support for the top two candidates is nearly evenly split. These states are critical battlegrounds where even a small shift in voter preference could change the outcome. For example, Arizona has the smallest margin, making it a highly competitive state. Otherwise, states like Washington, California, and South Dakota have wider margins, suggesting a more clear lead for one candidate. While they are still classified as battlegrounds due to the selected margin threshold, they are less competitive than states at the bottom.
```{r}
#| label: tbl-2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Predicted support percentages for Kamala Harris and Donald Trump in key competitive states, showing the anticipated winner and the percentage margin of support in each state."

@@

```
In @fig-figure2, We have figured out the key states that relatively important to the solutions of election. @tbl-2 presents the support percentages for Kamala Harris and Donald Trump across seven states, alongside a prediction of the winner based on the higher support percentage, and the margin of support difference between the two candidates. The table reveals that in several states (Arizona, Georgia, Nevada, North Carolina, and Pennsylvania), the margin between Kamala Harris and Donald Trump is extremely narrow (all under 2%). This tight margin indicates that these states are highly competitive, with neither candidate having a decisive lead. Such close races mean these states could easily swing in favor of either candidate depending on small shifts in public opinion or voter turnout. While Harris appears to have a slight edge in most of the states listed, the narrow margins mean that the race remains highly uncertain and dynamic.

@@

>>>>

# Load required libraries
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
library(arrow)

@@

# result

@@

The national average support percentages, along with other summary statistics for Donald Trump and Kamala Harris, are summarized in @tbl-1. This table presents average support, standard deviation, and the range of polling support values for each candidate, providing insights into the predicted national favorability for both candidates.

@@

# Plot the map showing support difference
ggplot(map_data, aes(long, lat, group = group, fill = support_diff)) +
  geom_polygon(color = "white") +
  scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0, 
                       name = "Support Difference\n(Harris - Trump)") +
  theme_minimal() +
  theme(legend.position = "right")
```

@fig-figure1 visualizes the difference in average polling support between Kamala Harris and Donald Trump across U.S. states. The map uses a color gradient to convey where each candidate has more support, with shades of blue indicating higher support for Harris, red indicating higher support for Trump, and white representing near-equal support levels. This visual provides a geographic perspective on the polling landscape, highlighting regional strongholds, competitive states, and areas of significant support advantage for each candidate.

@@

@fig-figure2 visualizes the polling margins between the top two candidates in various states. Each bar represents a state, with the length of the bar corresponding to the polling margin—the difference in polling percentage between the leading candidate and the runner-up. States are ordered by margin, from the narrowest at the bottom (indicating the closest contest) to the widest margin at the top. For instance, states like Arizona, Minnesota, and Michigan show extremely close polling margins, meaning that support for the top two candidates is nearly evenly split. These states are critical battlegrounds where even a small shift in voter preference could change the outcome. For example, Arizona has the smallest margin, making it a highly competitive state. Otherwise, states like Washington, California, and South Dakota have wider margins, suggesting a more clear lead for one candidate. While they are still classified as battlegrounds due to the selected margin threshold, they are less competitive than states at the bottom.

```{r}
#| label: tbl-2
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Predicted support percentages for Kamala Harris and Donald Trump in key competitive states, showing the anticipated winner and the percentage margin of support in each state."

@@

In @fig-figure2, We have figured out the key states that relatively important to the solutions of election. @tbl-2 presents the support percentages for Kamala Harris and Donald Trump across seven states, alongside a prediction of the winner based on the higher support percentage, and the margin of support difference between the two candidates. The table reveals that in several states (Arizona, Georgia, Nevada, North Carolina, and Pennsylvania), the margin between Kamala Harris and Donald Trump is extremely narrow (all under 2%). This tight margin indicates that these states are highly competitive, with neither candidate having a decisive lead. Such close races mean these states could easily swing in favor of either candidate depending on small shifts in public opinion or voter turnout. While Harris appears to have a slight edge in most of the states listed, the narrow margins mean that the race remains highly uncertain and dynamic.

@@

**Appendix A: Ipsos Polling Methodology**

\

**A.1 Population, Frame, and Sample**

**A1.1 Population**

Ipsos segments the target population into All Adults (A), Likely Voters (LV), and Registered Voters (RV) groups {RyanBest_2024}. The "All Adults" category represents the general adult population, offering broad insight into public sentiment. The "Likely Voters" group includes individuals estimated to vote based on past voting behavior or intention, providing a closer view of probable election outcomes. The "Registered Voters" segment covers those registered to vote, capturing eligible voters' opinions, even if they may not vote. Estimating "Likely Voters" involves assumptions based on behavioral factors that may not always align with actual turnout. As people’s intentions don’t always translate into action, thus may result in over-representation issue.

**A1.2 Frame**

The sampling frame used by Ipsos is the KnowledgePanel, a probability-based online panel {ABCNews_2024a}. Members of this panel are recruited via address-based sampling, which randomly selecting addresses from the US Postal Service’s Delivery Sequence File to create a probability-based panel {ABCNews_2024a}. This method ensures that each household in the sampling frame has a known and non-zero probability of being selected, providing comprehensive geographic coverage across the US and minimizes selection bias {ABCNews_2024a}. Additionally, Ipsos bridge the digital divide by providing internet access and tablets to panelists who otherwise lack connectivity, enabling participation from households that may not have regular internet access {ABCNews_2024a}. This approach reduces biases associated with digital access and enhances the inclusivity of the sample. However, the reliance on an online panel may still present some limitations, as it might partially exclude populations who may face challenges with technology, particularly older adults.

**A1.3 Sample**

Once members are part of the KnowledgePanel, Ipsos selects survey participants based on demographic quotas including sex, age, race/ethnicity, and region, and applies post-stratification weights to align with benchmarks from the Current Population Survey and American Community Survey {ABCNews_2024a}. Political engagement weighting includes factors like 2020 voting participation, improving representativeness for political polling. These weights are incorporated through a probability-proportional-to-size selection process, which assigns higher selection probabilities to underrepresented groups within the panel {ABCNews_2024a}. This approach helps ensure the sample reflects the diverse US population and improves its representativeness in polling results. While this isn't simple random sampling at this stage, the initial framework and recruitment, weighted selection process ensure that the panel and samples are broadly representative.

**A.2 Sample Recruitment**

Ipsos recruits members for its KnowledgePanel using address-based sampling, sourced from the US Postal Service’s Delivery Sequence File {\@ABCNews_2024a}. This probability-based method allows each household to be randomly selected, increasing the panel’s representativeness across geographic and demographic groups {\@ABCNews_2024a}. To improve accessibility, Ipsos provides tablets and internet connections at no cost to those without internet access, helping to include lower-income or otherwise underserved populations and reducing the digital divide {\@ABCNews_2024a}. Despite these efforts, the approach has some limitations. While address-based sampling reaches a wide range of households, certain groups—like older adults with limited digital literacy—may still be less likely to participate, potentially impacting sample diversity. Also such sample recruitment approach can be expensive considering address-based sampling and inclusion measures. Nonetheless, Ipsos’ recruitment methods, combined with inclusivity measures, provide a strong foundation for building a representative panel.

**A.3 Sampling Approach and Trade-offs**

**A.3.1 Strengths**

Address-based sampling creates a representative sample across regions and demographics, ensuring that each household has a known, non-zero chance of selection. Unlike non-probability approach, such probability-based approach helps achieve a representative sample of the US population across various regions and demographics, improves inclusion of hard-to-reach populations and reduce selection bias {\@callegaro2014online}. Further probability-proportional-to-size approach balances the sample by ensuring adequate representation of underrepresented groups {\@keyfitz1951sampling}.

2\. Ipsos’ use of demographic quotas and post-stratification weights aligns samples with the broader population {\@ABCNews_2024a}.

3\. Multilingual surveys and internet access provision enhance inclusivity {\@ABCNews_2024a}.

4\. Ipsos incorporates multiple likely voter models, incorporating factors like voter registration, intention to vote, and past voting behavior to adjust pre-election polling relevance, increases accuracy {\@ABCNews_2024a}.

5.Ipsos includes design effects in the margin of error, enhancing poll reliability transparency {\@ABCNEWS/IPSOS}.

**A.3.2 Limitations**

1\. As \@panzeri2008sampling revels, using a sampling frame does not guarantee the elimination of sampling bias, if the target population is incorrectly defined or based on outdated or incomplete information, certain segments of the population may be excluded. Ipsos aligns its sample with demographic benchmarks from sources like the Current Population Survey and the American Community Survey {\@ABCNews_2024a}. Outdated benchmarks or 2020 voting data may not reflect current behaviors.

2\. Members of the KnowledgePanel must opt-in to join and remain in the panel, which can lead to self-selection bias. Individuals who agree to participate in ongoing surveys might differ in unmeasured ways from those who do not, potentially skewing the results.

3\. Weighting for political engagement based on past elections assumes stable voter behavior, which may not account for shifting demographics or emerging issues {\@ABCNews_2024a}.

4\. Although Ipsos provides internet access and tablets to those without connectivity, some individuals may still lack the digital literacy needed to engage fully with online surveys. Older adults and those with lower levels of education or comfort with technology may participate differently, leading to potential response biases within these groups.

5\. Probability-based panels involve higher costs and resources due to recruitment and maintenance, particularly with inclusive measures {\@callegaro2014online}.

**A.4 Non-response Handling**

Ipsos sends initial reminders to panelists who do not respond to survey invitations, with a second reminder for harder-to-reach participants, allowing multiple opportunities to increase response rates {\@ABCNews_2024a}. In post-stratification, Ipsos applies weighting adjustments to mitigate nonresponse bias {\@ABCNews_2024a}. Additionally, Ipsos enforces strict quality control by removing respondents who show low engagement, such as those who skip many questions or complete surveys at unusually fast speeds to improve the reliability of the survey results {\@ABCNews_2024a}.

**A.5 Questionnaire Design**

**A.5.1 Strengths**

1\. Ipsos uses standardized and pre-tested questions to ensure consistency and clarity. This approach helps maintain reliability and accuracy by identifying and addressing potential issues in question design before full deployment {\@ABCNEWS/IPSOS}.

2\. Ipsos uses comprehensive likely voter models that consider factors like voter registration, voting intention, engagement with key issues, and carefully crafted question wording for different population (A, LV, RV), reflecting voter behaviors accurately and minimize ambiguity {\@ABCNEWS/IPSOS}.

3\. Adapting questionnaires to current issues enhances pre-election prediction relevance {\@ABCNEWS/IPSOS}.

4\. Ipsos protects respondent privacy through anonymization, secure data handling, confidentiality assurances, aggregation of data in reporting, and informed consent, ensuring ethical standards in data collection {\@LangerResearchAssociates}.

**A.5.2 Limitations**

1\. Detailed models and questions may cause survey fatigue among less-engaged respondents {\@sinickas2007finding}.

2\. Ipsos surveys may face context and order effects, influencing responses based on question order {\@vmartin2006survey}.

3\. Reliance on likely voter traits could risk underrepresentation of groups perceived as unlikely voters, posing ethical considerations.

**Appendix B: Idealized Methodology for US Presidential Election Forecasting Using Stratified Sampling**

**B.1 Overview**

This appendix details a methodology for forecasting the US presidential election within a \$100,000 budget. By using a stratified sampling approach, we aim to ensure accurate representation across key demographic and geographic subgroups. The methodology includes respondent recruitment, data validation, poll aggregation, and a structured survey design. A link to the survey on Google Forms and a copy of the survey questions are included.

**B.2 Budget allocation**

**Online Panel Access:** \$30,000

Access to pre-recruited, diverse online panels, allowing targeted sampling and demographic stratification.

**Telephone Surveys with AI Assistance:** \$20,000

Use computer-generated random sampling for phone outreach, including AI-assisted interviews to enhance consistency, focusing on hard-to-reach demographics.

**Incentives for Respondents:** \$15,000

Small incentives for survey participants, partially funded by the panel provider, to improve response rates.

**Survey Platform (Google Forms):** \$0

Google Forms is free for basic use, allowing cost-effective data collection with skip logic to reduce respondent fatigue.

**Data Validation and Quality Control:** \$5,000

Includes demographic validation, speed checks, and attention checks to ensure high-quality responses and accuracy.

**Post-Stratification Weighting:** \$5,000

Application of weights to adjust for minor demographic imbalances and align with population benchmarks.

**Poll Aggregation and Analysis:** \$15,000

Use Bayesian updating and statistical analysis to combine results with other reputable polls, enhancing accuracy.

**Reporting and Presentation:** \$8,000

Preparation of a detailed report, including visualizations, summaries, and a 95% confidence interval to indicate forecast precision.

**Contingency Fund:** \$7,000

Reserve for unforeseen costs or additional recruitment needs.

\
**B.3 Sampling Approach**

We will implement stratified sampling method, a form of probability sampling incorporating various demographic categories, ensuring proportional representation of each subgroup within the sample, thereby improving forecast accuracy by addressing potential voter turnout imbalances {\@alexander2023telling}.

**B.3.1 Define the strata**

The population will be divided into distinct, mutually exclusive subgroups, or “strata,” based on key demographic variables: age, gender, race/ethnicity, education, income, and geographic region. Each stratum will be sampled proportionally to its representation within the US voter population, ensuring that the sample closely aligns with national demographics. Here we want to keep the strata relatively general to avoid potential over-fitting issues.

**B.3.2 Define the sample size**

A sample size of 5,000 respondents will ensure adequate representation across strata, with a margin of error of ±2%, sufficient for accurate subgroup analysis.

**B.3.3 Recruitment Strategy**

1.Through partnering with other online panel partnership, we access large, diverse panels where participants are pre-recruited and actively engaged. These panels allow for stratification according to specific demographic criteria, improving efficiency and precision.

2\. Online panels typically offer incentives to their participants, funded by the panel provider or through the survey budget, reducing direct incentive costs.

3.Utilize computer-generated random sampling of phone numbers to reach respondents via both landlines and mobile phones, with cost control achieved by targeting specific geographic regions or demographic groups. Integrate an AI interviewer to minimize potential enumerator-related issues, enhancing consistency and efficiency. Telephone surveys are particularly effective for reaching older populations or those less likely to engage online.

**B.4 Data Collection and Survey Design**

The survey will be hosted on Google Forms for cost-effective data collection. Google Forms  also offers skip logic, which will reduce survey Fatigue and improve response accuracy.

**B.4.1 Survey Content**

The survey will include questions to capture:

1.  **Screening Questions:** US citizenship.

2.  **Demographics** – age, sexual orientation and gender identity, race/ethnicity, education, income, region.

3.  **Voting Intentions** – likelihood of voting, candidate preference.

4.  **Political Engagement** – previous voting behavior, issue importance, and whether respondents have been personally contacted by the Harris or Trump campaign specifically asking for their vote.

5.  **Key Election Issues** – opinions on topics like healthcare, economy, education, and immigration.

**B.4.2 Survey Link**

https://docs.google.com/forms/d/e/1FAIpQLScFPzyAHVMJ_kcg4gYC-tvea1M1UKBb-wmB6dMSeXB5bWgMQA/viewform?usp=sf_link

Each respondent will see an introductory section outlining the survey’s purpose, instructions, confidentiality safeguards, and contact details.

**B.5 Data Validation and Post-Survey Processing**

B.5.1 Quality Control Measures

1\. Demographic Validation – Responses will be checked to ensure quotas for each stratum are met.

2\. Speed Check – Responses completed less than 10% of the time will be flagged and possibly removed to ensure quality.

3\. Attention Checks – Simple questions (e.g., “yes or no questions”) will validate respondent engagement.

**B.5.2 Post-Stratification Weighting\
**Weights will be applied to correct minor demographic imbalances, aligning the sample with population benchmarks.

**B.5.3 Poll Aggregation and Forecasting\
**To enhance robustness, results will be combined with other reputable polls using Bayesian updating, with greater weight given to more recent polls and those with larger sample sizes. A 95% confidence interval will be provided to indicate forecast precision, and design-effect adjustments will be applied to refine the margin of error.

**B.6 Copy of the Survey**

**1. Are you a US citizen?**

-   Yes

-   No

**2. What is your age?**

-   18–24

-   25–34

-   35–44

-   45–54

-   55–64

-   65+

**3. What sex were you assigned at birth, on your original birth certificate?**

-   Female

-   Male

**4. How do you currently describe yourself (check all that apply)?**

-   Female

-   Male

-   Transgender

-   Other \[free-text\]

**5. Which of the following best represents how you think of yourself?”**

-   Gay or lesbian

-   Straight, that is not gay or lesbian

-   Bisexual

-   I don’t know

-   Other \[free-text\]

**6. What is your race/ethnicity?**

-   White

-   Black or African American

-   Hispanic or Latino

-   Asian

-   Other \[free-text\]

**7. What is the highest level of education you have completed?**

-   High school or less

-   Some college

-   Bachelor’s degree

-   Graduate degree

**8. What is your household income?**

-   Less than \$50,000

-   \$50,000–\$99,999

-   \$100,000–\$149,999

-   \$150,000 or more

**9. What is your geographic region?**

-   Northeast (CT, ME, MA, NH, NJ, NY, PA, RI, VT)

-   Midwest (IL, IN, IA, KS, MI, MN, MO, NE, ND, OH, SD, WI)

-   South (AL, AR, DE, DC, FL, GA, KY, LA, MD, MS, NC, OK, SC, TN, TX, VA, WV)

-   West (AK, AZ, CA, CO, HI, ID, MT, NV, NM, OR, UT, WA, WY)

**10. How likely are you to vote in the upcoming election?**

-   Absolutely certain to vote

-   Probably will vote

-   Chances are 50/50

-   Less likely to vote

-   Already voted

**11. If the election were held today, who would you vote for? (IF ALREADY VOTED) Confidentially and for Statistics purpose only, who did you vote for?**

-   Harris

-   Trump

-   West

-   Stein

-   Oliver

-   Someone else

-   Undecided

**12. Did you vote in the 2020 presidential election?**

-   Yes

-   No

**13. How closely are you following the 2024 presidential race?**

-   **Very closely**

-   **Fairly closely**

-   **Somewhat closely**

-   **Not very closely**

-   **Not at all**

**14. Have you personally been contacted by the Harris or Trump campaign specifically asking for your vote (not including fundraising appeals)? (Check all that apply)**

-   Harris

-   Trump

-   No one

**15. What issues are most important to you in this election? (Select top 3)**

-   Economy

-   Healthcare

-   Education

-   Climate Change

-   Immigration

-   National Security

-   Social Justice

-   Other \[free-text\]
